Response to Reviewers $Rev^1$

### 2020-04-02 ICT_Frontiers_rev202001_reply.tex
Updates from Overleaf

    	\begin{ans}
    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear and readable. 
    	\end{ans}

@@

    	\begin{ans}
    		We thank the reviewer for this question. We agree that this point is not clear in our original manuscript.

    		Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow Y )$) and informational closure ($J_{t}(X \rightarrow Y )=0$) to both graphs.

    		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about NTIC and consciousness (informational closure from a process to its environment) in an integrated framework.

>>>>

    	\begin{ans}
    		We have invited a native English speaker for proofreading. Please inform us if it is still not clear or unreadable. 
    	\end{ans}

@@

    	\begin{ans}
    		We thank the reviewer for this question. We agree that this point is not clear in our original manuscript. Even though the Bayesian graphs for the system-environment dependency are different from the one for the micro-macro level dependency, we apply the same definitions of information flow ($J_{t}(X \rightarrow Y )$) and informational closure ($J_{t}(X \rightarrow Y )=0$) to both graphs.

    		This is a critical assumption in ICT because applying the same definition of informational closure in both scenarios can solve the scale problem of consciousness (informational closure from one level to other levels) and construct our hypothesis about the relation between NTIC and consciousness (informational closed from a process to its environment) in an integrated framework.
